
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #4}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Aviral Srivastava} \\ \vspace{1pt}
    Lucknow, Uttar Pradesh \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 9140212738 ~ \href{mailto:aviralji4@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{aviralji4@gmail.com}} ~
    \href{https://www.linkedin.com/in/aviral-srivastava-07b1a4202/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/aviral-srivastava-07b1a4202/}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KIET Group of Institutions}{Sept 2020 - Present}
      {Bachelor of Technology in Computer Science and Engineering (SGPA of 9.03)}{Ghaziabad, Uttar Pradesh, India}
  \resumeSubHeadingListEnd
  \vspace{-15pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lucknow Public School}{2018 - 2019}
      {Senior Secondary (93.6\%)}{Lucknow, India}
  \resumeSubHeadingListEnd
  \vspace{-15pt}
    \resumeSubHeadingListStart
    \resumeSubheading
      {Lucknow Public School}{2016 - 2017}
      {Secondary (CGPA of 10.0)}{Lucknow, India}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cyethack Solutions }{Sept 2022 -- Present}
      {Product Developer Intern}{Online}
      \resumeItemListStart
        \resumeItem{Created a web based backend + frontend tool (using MERN stack) to interact, and see all the information related to the Web reconnaissance. }
    \resumeItemListEnd
    
    \resumeSubheading
      {C3i Hub, Indian Institute of Technology, Kanpur }{July 2022 -- Oct 2022}
      {Summer Security Research Intern}{Kanpur, India}
      \resumeItemListStart
        \resumeItem{Set up the server with Elasticsearch, Kibana and Logstash, and set up Apache Kafka to be used with Logstash. }
        \resumeItem{Scraped tweets based on keywords, identified sources and real time from twitter (using tweepy). Also collected data from telegram using telethon - fetched live messages, implemented filtering based on keywords, channel search, extracting channel users info.}
        \resumeItem{Analysis of the collected information related to recognized illegal content using Natural Language Processing. }
        \resumeItem{Maintained project documentation and the GitHub repository. }
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Py-LMDC} $|$ \emph{Python} $|$ {github.com/godofgeeks23/python-LMDC}}{January 2019}
          \resumeItemListStart
            \resumeItem{A ML based Linux Malware Detection and Classification
System built using Python.}
          \resumeItemListEnd
    \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Docs Image Cleaner} $|$ \emph{Python, Google Teachable Machine}  $|$ {github.com/godofgeeks23/SC\_Document\_Img\_Cleaner}}{January 2019}
          \resumeItemListStart
            \resumeItem{A ML based tool to free up space occupied by document
images and screenshots.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%
%-----------Achievements-----------
\section{Achievements [Add all kind of achievements that shows your skills]}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \resumeItemListStart
        \resumeItem{Highest rating of \textbf{ xxxx} at Codeforces, which is the top site in terms of participation of programmers across globe.}
        \resumeItem{Ranked under \textbf{xyz} at Codechef which ranks among the top sites for competitive programmers. Highest rating of 2299 and rated \textbf{6*}. }
        \resumeItem{Qualified the prestigious ACM-ICPC regionals \textbf{thrice} and ranked Z in one of the attempts. }
        \resumeItem{Secured all India rank of \textbf{r, s, t} respectively in Codechef's Long Challenge in the month of February, April and May xyzh among 12k+ participants.}
        \resumeItem{Secured all India rank of \textbf{uh} in TCS codevita 2019.}
        \resumeItem{Written over \textbf{0987643} articles at Geeksforgeeks, most of them being on Data Structure and Algorithms}
        \resumeItem{Solved more than 2000+ problems across platforms.}
        \resumeItem{Awarded with Geek of the year accolade from GeeksforGeeks for contribution to the community. \href{https://www.geeksforgeeks.org/geek-of-the-year/}{(Link)} }
      \resumeItemListEnd
 \end{itemize}
 \vspace{-16pt}
 
 %
%-----------Profile Links-----------
\section{Profile Links}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \resumeItemListStart
        \resumeItem {\href{https://www.codechef.com/users/striver_79/}{Codechef}}
        \resumeItem {\href{https://codeforces.com/profile/striver_79}{Codeforces}}
        \resumeItem {\href{https://leetcode.com/striver_79/}{Leetcode}}
        \resumeItem {\href{https://auth.geeksforgeeks.org/user/Striver/articles}{GeeksforGeeks}}
      \resumeItemListEnd
 \end{itemize}
 \vspace{-16pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills [Don't overflood here]}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Python, Java, HTML/CSS, JavaScript, SQL} \\
     \textbf{Technologies/Frameworks/Libraries}{: Spring, Junit, ReactJS} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}


